Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-19 WSSSPE3/report/wg_appendix_best_practices.tex
Update wg_appendix_best_practices.tex
Minor update to group participants
misc symbol corrections

\begin{itemize}
\item Abani Patra -- University at Buffalo
\item Sandra Gesing -- University of Notre Dame
\item Neil Chue Hong -- Software Sustainability Institute
\item Gregory Tucker -- University of Colorado at Boulder
\item Birgit Penzens -- California State University Long Beach
\item Abigail Cabunoc Mayes -- Mozilla Foundation
\item Frank L\"{o}ffler -- Louisiana State University 
\item Colin Venter --  University of Huddersfield
\item Lorraine Hwang -- UC Davis 
\item Sou-Cheng Choi -- NORC at the University of Chicago \&  Illinois Institute of Technology
\item Suresh Marru -- Indiana University
\item Don Middleton -- NCAR 
\item Daniel S. Katz --  University of Chicago \& Argonne National Laboratory
\item Kyle Niemeyer -- Oregon State University
\item Jeffrey Carver -- University of Alabama
\item Dan Gunter -- LBNL
\item Alexander Konovalov -- University of St Andrews
\item Tom Crick --  Cardiff Metropolitan University

@@

\item Dimensions of sustainability -- economic, technical, environmental,
and obsolescence.
%declining interest in primary application area), \katznote{not sure what the
%prev. comment goes with} social.

>>>>

\begin{itemize}
\item Abani Patra -- University at Buffalo
\item Sandra Gesing -- University of Notre Dame
\item Neil Chue Hong -- Software Sustainability Institute
\item Gregory Tucker -- University of Colorado at Boulder
\item Birgit Penzenstadler -- California State University Long Beach
\item Abigail Cabunoc Mayes -- Mozilla Foundation
\item Frank L\"{o}ffler -- Louisiana State University 
\item Colin C. Venters --  University of Huddersfield
\item Lorraine Hwang -- UC Davis 
\item Sou-Cheng Choi -- NORC at the University of Chicago \&  Illinois Institute of Technology
\item Suresh Marru -- Indiana University
\item Don Middleton -- NCAR 
\item Daniel S. Katz --  University of Chicago \& Argonne National Laboratory
\item Kyle Niemeyer -- Oregon State University
\item Jeffrey Carver -- University of Alabama
\item Dan Gunter -- LBNL
\item Alexander Konovalov -- University of St Andrews
\item Tom Crick --  Cardiff Metropolitan University

@@

\item Dimensions of sustainability: economic, technical, environmental,
and obsolescence.
%declining interest in primary application area), \katznote{not sure what the
%prev. comment goes with} social.

### 2016-01-19 WSSSPE3/report/wg_appendix_funding_spec_expert.tex
misc symbol corrections

``Are you an RSE or a RA?'' is not properly a binary question. Most of
us sit at different points on that spectrum, and move along it during our
careers (usually from RA to RSE -- examples of movement in the other direction
from readers would be welcomed). Either way, the label ``Research Software
Engineer'' is now starting to have some power. Many scientists do not want to be
writing code; some do, to varying degrees. These groups can usefully support
each other.

>>>>

``Are you an RSE or a RA?'' is not properly a binary question. Most of
us sit at different points on that spectrum, and move along it during our
careers (usually from RA to RSE---examples of movement in the other direction
from readers would be welcomed). Either way, the label ``Research Software
Engineer'' is now starting to have some power. Many scientists do not want to be
writing code; some do, to varying degrees. These groups can usefully support
each other.

### 2016-01-19 WSSSPE3/report/wg_main_eng_design.tex
misc symbol corrections

\subsubsection{Landing Page}
In the absence of a landing page, the Principles for Software Engineering Design for Sustainable Software working group requests an email be sent to Birgit Penzenstadler\footnote{email: \href{mailto:birgit.penzenstadler@csulb.edu}{birgit.penzenstadler@csulb.edu}} and Colin C. Venters\ to find out more about the group's efforts and how to participate.

>>>>

\subsubsection{Landing Page}
In the absence of a landing page, the Principles for Software Engineering Design for Sustainable Software working group requests an email be sent to Birgit Penzenstadler\footnote{email: \href{mailto:birgit.penzenstadler@csulb.edu}{birgit.penzenstadler@csulb.edu}} and Colin C.\ Venters\ to find out more about the group's efforts and how to participate.
